When an animal learns to associate a stimulus $S^+$ with reward, this learning may generalize to other, novel stimuli. 
The greater the physical similarity between $S^+$ and the novel stimulus, the greater the generalization and presumed perceptual similarity. 
Using generalization to establish perceptual similarity can provide important predictions for olfactory coding in the CNS. 
However, perceptual relatedness among olfactory stimuli is hard to determine, because physiochemical similarity does not always predict similar behavioral responses. 
Natural odors are typically mixtures of multiple components, which pose a further challenge when estimating perceptual similarities.  
Similarity between mixtures is presumably determined by similarity of the corresponding components.
However, it is unclear how mixture similarity is computed by the olfactory system.  
To investigate this problem, we trained mice to associate a binary reference mixture ($S^+$) with reward, and we then tested response probability to different binary test mixtures.  
Across 5 experiments, we parametrically varied the mixtures in several ways to assess generalization as these parameters were varied.  
We then evaluated three candidate approaches for evaluating perceptual similarity, according to their correspondence with the data from the 5 experiments.  
We found the best fit for a model in which, for each component \textit{A} of the $S^+$, only the similarity of the ``nearest'' component \texit{A*} of a test mixture was used to predict behavioral response, with nearness determined by physiochemical distance.  
We conclude that the olfactory system may deemphasize or discard information about other components not perceptually ``near'' enough to any of those in the $S^+$.  
    
    